Incentivizing Exploration with Unbiased History

### 2018-11-02 3level.tex
One more minor edit.

The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $S$ has the following property:
\begin{align}\label{eq:group-defn}
\text{all nodes in $S$ are connected to the same nodes outside of $S$, but not to one another.}
\end{align}

>>>>

The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $G$ has the following property:
\begin{align}\label{eq:group-defn}
\text{all nodes in $G$ are connected to the same nodes outside of $G$, but not to one another.}
\end{align}
